\section*{CHAPTER 4: EVALUATION AND CONCLUSION}
\addcontentsline{toc}{section}{\numberline{}CHAPTER 4: EVALUATION AND CONCLUSION}
\setcounter{section}{4}
\setcounter{subsection}{0}
\setcounter{figure}{0}
\setcounter{table}{0}

\subsection{System Evaluation and Results}

The development and deployment of the FootField SaaS platform have successfully met the initial project objectives. The system provides a robust, multi-tenant environment capable of securely hosting numerous football facility owners on a single unified infrastructure. 

Key achievements include:
\begin{itemize}
    \item \textbf{Operational Efficiency:} The time-grid schedule viewer and automated booking system have drastically reduced the time spent on manual scheduling and completely eliminated double-booking errors.
    \item \textbf{Customer Experience:} The integration of the Google Gemini AI chatbot offers a unique, conversational interface for checking availability and making bookings, significantly enhancing user engagement compared to traditional web forms.
    \item \textbf{Financial Accuracy:} The VNPay integration ensures secure, instantaneous transaction processing, while the automated invoicing and occupancy rate calculations provide facility owners with clear financial insights.
    \item \textbf{Mobile Accessibility:} The Capacitor-wrapped Android applications successfully bridge the gap between software and hardware, allowing staff to perform rapid QR code check-ins directly on the field.
\end{itemize}

Performance testing on the Render and Aiven cloud environments indicates that the Monolithic Hybrid architecture maintains fast response times and stable database connections even under simulated concurrent user loads.

\subsection{Limitations}

Despite the successes, the current iteration of the system has some limitations. The AI Chatbot, while intelligent, relies on the Google Gemini API, meaning its response time is subject to network latency and Google's API rate limits. Additionally, the system currently only supports VNPay; integrating other popular e-wallets like MoMo or ZaloPay would provide more options for users.

\subsection{Future Development Directions}

To further enhance the platform, several features are planned for future development:
\begin{enumerate}
    \item \textbf{IoT Integration:} Connecting the booking system to IoT smart switches to automatically turn on/off the football field lighting based on the booking schedule and QR check-in status.
    \item \textbf{Advanced Analytics:} Implementing machine learning algorithms on the tenant dashboards to predict peak hours and suggest optimal pricing strategies based on historical occupancy data.
    \item \textbf{Expanded Payment Options:} Integrating additional payment gateways and introducing a customer wallet system for recurring players.
\end{enumerate}

\subsection{Conclusion}

In conclusion, the FootField platform demonstrates the immense potential of applying modern SaaS architectures, Artificial Intelligence, and mobile integration to traditional service industries. By providing a comprehensive, scalable, and user-friendly solution, this project successfully bridges the gap between technology and sports facility management, laying a strong foundation for future commercial deployment.